---
title: "LymphomaSubtype"
author: "Makoto"
date: "17/11/2020"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LymphomaSubtype

<!-- badges: start -->
<!-- badges: end -->

The goal of `LymphomaSubtype` is to provide an user with an easy
breakdown of each subtypes of lymphoma. As of Nov 17th, 2020, the specific disease subtypes are based on [here](https://www.llscanada.org/lymphoma/non-hodgkin-lymphoma/diagnosis/nhl-subtypes) and their categories are based on [here](https://www.lymphomacoalition.org/lymphomas/lymphoma-subtypes).

## How this data set was created

First, I created the skeleton of the package by 

```{r eval = FALSE}
library(usethis)
usethis::create_package(path = LymphomaSubtypes)
```

`Lymphoma` data set was created manually by SOURCE_OF_DATA.

I added details to the package using `devtools` and `usethis` packages.

```{r eval = FALSE}
usethis::use_readme_rmd()      # To create a README.md file
usethis::use_mit_license()     # To add license
devtools::document()           # To document and update a package
usethis::use_package()         # To add dependency
```

## Installation

You can install the development version from (GitHub)[LINK_FOR_MY_GITHUB] with:

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github(ma5ki4/LymphomaSubtype)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r eval = FALSE}
library(LymphomaSubtype)
lymphoma
```

## Code of Conduct
  
Please note that the LymphomaSubtypes project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
